\SW: II. Did we beat the lens finding robots in CFHTLS?

### 2014-09-08 doc/sw-cfhtls.tex
Solved it - as in RG's email, you have to select T06 as well as q_flag = 3 or 2. Closed #69

At galaxy-scales, we focus on two primary lens searches. The RingFinder
\citep{Gavazzi2014} was used for finding compact rings or arcs around centers
of isolated and massive early-type galaxies. By subtracting the PSF-matched
$i$-band images from the $g$-band images, the algorithm looks for excess flux
in the bluer $g$-band. An object detector measures the properties of these
residual blue features, and candidates meeting length-width ratio and
tangential alignment criteria are then visually inspected to form the final
sample. \citet{Gavazzi2014} first selected some 638,000 targets as either
photometrically-classified early type galaxies, or objects selected to have
red centers and blue outer parts. 14370 were found to show detectable blue
residuals, and 2524 were visually inspected, having passed the automatic
feature selection process. This led to a sample of 42 good quality
(\texttt{q\_flag} = 3) and 288 medium quality (\texttt{q\_flag} = 2) lens
candidates. In addition to this well defined sample, \citet{Gavazzi2014}
reported a further 71 serendipitously detected lens candidates. 
From this sample of ``RingFinder candidates,'' the SL2S team found, during
their follow-up campaign, 39 confirmed lenses (and 17 promising
candidates). We use this sample of 39 ``confirmed RingFinder lenses'' in our
completeness analysis.

\todo{Phil}{check with RG about SQL queries for the RF candidates.
\texttt{q\_flag = 3} returns 55, not 42, systems, and 
\texttt{q\_flag = 3} returns 346, not 288, systems. This is all issue \#69}

>>>>

At galaxy-scales, we focus on two primary lens searches. The RingFinder
\citep{Gavazzi2014} was used for finding compact rings or arcs around centers
of isolated and massive early-type galaxies. By subtracting the PSF-matched
$i$-band images from the $g$-band images, the algorithm looks for excess flux
in the bluer $g$-band. An object detector measures the properties of these
residual blue features, and candidates meeting length-width ratio and
tangential alignment criteria are then visually inspected to form the final
sample. \citet{Gavazzi2014} first selected some 638,000 targets as either
photometrically-classified early type galaxies, or objects selected to have
red centers and blue outer parts, from the T06 CFHTLS data release catalogs. 
14370 were found to show detectable blue residuals, and 2524 were visually
inspected, having passed the automatic feature selection process. This led to
a sample of 42 good quality (\texttt{q\_flag} = 3) and 288 medium quality
(\texttt{q\_flag} = 2) lens candidates. In addition to this well defined
sample, \citet{Gavazzi2014} reported a further 71 serendipitously detected
lens candidates.  From this sample of ``RingFinder candidates,'' the SL2S team
found, during their follow-up campaign, 39 confirmed lenses (and 17 promising
candidates). We use this sample of 39 ``confirmed RingFinder lenses'' in our
completeness analysis.
